Variational Monte Carlo on Bosonic Systems

### 2018-04-06 project_1/article/article.tex
Spell check summary remarks

    In this study we have built a functional variational Monte Carlo solver framework for
    a gas following Bose-Einstein statistics confined in an elliptic trap. Monte Carlo
    methods is a broad class of computational algorithms, whereas the variational
    Monte Carlo is a subset. Other applications of such methods within the physical
    sciences includes, but is not limited to, quantum chromodynamics, the modeling of
    aearodynamic forms, particle physics detector design and galaxy evolution.
    Needless to say, Monte Carlo method is a valuable tool for a computational physicist.

    To prove the
    validity of the framework we tested it against an analytically solved case, an ideal
    non-interacting system. Thereafter we have shown how our implementation can
    handle large systems of interacting particles and perturbed traps. Even though
    this study is somewhat theoretic in nature, we have discussed the possibility of
    expanding our machinery to a case bearing a larger resemblance to a system
    found in nature. To this end we have computed one-body densities for the
    interacting system, which can be compared to real physical properties as
    measured in an experiment.

>>>>

    In this study we have built a functional variational Monte Carlo solver
    framework for a gas following Bose-Einstein statistics confined in an
    elliptic trap. Monte Carlo methods is a broad class of computational
    algorithms, whereas the variational Monte Carlo is a subset. Other
    applications of such methods within the physical sciences includes, but is
    not limited to, quantum chromodynamics, the modeling of aerodynamic forms,
    particle physics detector design and galaxy evolution.  Needless to say,
    Monte Carlo methods is a valuable tool for a computational physicist.

    To prove the validity of the framework we tested it against an analytically
    solvable case, an ideal non-interacting system. Thereafter we have shown how
    our implementation can handle large systems of interacting particles and
    perturbed traps. Even though this study is somewhat theoretic in nature, we
    have discussed the possibility of expanding our machinery to a case bearing
    a larger resemblance to a system found in nature. To this end we have
    computed one-body densities for the interacting system, which can be
    compared to real physical properties as measured in an experiment.
